### 2008-12-21 talk/ecoop2009/benchmarks.tex
changed sentence which Antonio does not like

Table \ref{tab:factorial-fibo} shows the seconds spent to calculate
the factorial and Fibonacci for various $n$.  As we can see, for small values
of $n$ the time spent running the JIT compiler is much higher than the time
spent to simply interpret the program.  This is an expected result, as till
now we only focused on optimizing the compiled code, not the compilation
process itself.

On the other hand, to get meaningful timings we had to use very high values of
$n$.  This means that the results are incorrect due to overflow, but since all
the runnings overflow in the very same way, the timings are still
comparable. \anto{I think we should rephrase this sentence}.  For $n$ greater
than $10^7$, we did not run the interpreted program as it would have took too
much time, without adding anything to the discussion.

>>>>

Table \ref{tab:factorial-fibo} shows the seconds spent to calculate
the factorial and Fibonacci for various $n$.  As we can see, for small values
of $n$ the time spent running the JIT compiler is much higher than the time
spent to simply interpret the program.  This is an expected result
which, however, can be improved once we will have time
to optimize compilation and not only the generated code.

On the other, for reasonably high values of $n$ we obtain very good
results, which are valid despite the obvious overflow, since the 
same operations are performed for all experiments.
For $n$ greater than $10^7$, we did not run the interpreted program as it would have took too
much time, without adding anything to the discussion.
